---
title: "Average_HR_Visualization"
author: "Thomas FitzGerald"
date: "2024-05-21"
output: html_document
---

```{r setup, include=FALSE}
#library(meteoForecast)
library(tidyverse)
library(readxl)
library(dplyr)
library(plotly)
library(ggplot2)
library(ggridges)
library(stats)
library(multcomp)
library(emmeans)
library(lsmeans)

library(stringr)
library(lubridate)
```

```{r}
df.weather <- read.csv('C:\\Users\\Thoma\\OneDrive\\Desktop\\Farm_1\\weather.csv')
df.hr <- read.csv('C:\\Users\\Thoma\\OneDrive\\Desktop\\Farm_1\\cow_HR_avg_bpm_3.csv')
```


```{r}
df.weather <- df.weather %>%
  mutate(Date=as.POSIXct(Date,format=c("%m/%d/%Y")))
df.hr <- df.hr %>%
  mutate(Date=as.POSIXct(Date,format=c("%m/%d/%Y")))
df.hr %>% arrange(Date)
```
```{r}
#df.weather %>% mutate(Min=((Min-32)*(5/9)),
                           #Avg=((Avg-32)*(5/9)),
                           #Max=((Max-32)*(5/9)))

ggplot(data=df.weather %>% mutate(Min=((Min-32)*(5/9)),
                           Avg=((Avg-32)*(5/9)),
                           Max=((Max-32)*(5/9))), aes(x=Date)) +
  geom_smooth(aes(y=Avg),se=F) +
  geom_point(aes(y=Avg),size=3) +
  geom_segment(aes(x=Date,xend=Date,y=Min,yend=Max),linetype='dashed') + #Range
  geom_segment(aes(x=Date-hours(6),xend=Date+hours(6),y=Min,yend=Min)) + #MinLine
  geom_segment(aes(x=Date-hours(6),xend=Date+hours(6),y=Max,yend=Max)) + #MaxLine
  geom_vline(xintercept=as.POSIXct('2024-10-04'), linetype='dotted') + 
  geom_vline(xintercept=as.POSIXct('2024-10-07'), linetype='dotted') +
  ylab("Temperature Range(C)") +
  theme_classic()
  #annotate("text",x=as.Date('2024-10-06'),y=35,label="Training") +
  #annotate("text",x=as.Date('2024-10-09'),y=35,label="Post-Training")
```

```{r}

df.hr.UTR <- df.hr %>% subset(Group=='UTR') %>% mutate(Date=Date-hours(3))
df.hr.TR <- df.hr %>% subset(Group=='TR') %>% mutate(Date=Date+hours(3))

ggplot(data=df.hr, aes(x=Date)) +
  #geom_smooth(data=df.hr.UTR,aes(y=mean),color="blue",se=F) +
  #geom_smooth(data=df.hr.UTR,aes(y=mean),color="blue",method=lm) +
  geom_smooth(data=df.hr.TR,aes(y=mean),color="red",se=F) +
  geom_smooth(data=df.hr.TR,aes(y=mean),color="red",method=lm) +
  geom_jitter(data=df.hr.UTR,aes(y=mean),size=2,color="blue",width = 2000) +
  geom_jitter(data=df.hr.TR,aes(y=mean),size=2,color="red",width = 2000) +

  #geom_segment(aes(x=Date,xend=Date,y=Min,yend=Max),linetype='dashed') +
  #geom_segment(aes(x=Date-hours(6),xend=Date+hours(6),y=Min,yend=Min)) +
  #geom_segment(aes(x=Date-hours(6),xend=Date+hours(6),y=Max,yend=Max)) +
  geom_vline(xintercept=as.POSIXct('2024-10-04'), linetype='dotted') +
  geom_vline(xintercept=as.POSIXct('2024-10-07'), linetype='dotted') +
  ylab("Heart Rate (bpm)") +
  theme_classic()
  #annotate("text",x=as.Date('2024-10-06'),y=35,label="Training") +
  #annotate("text",x=as.Date('2024-10-09'),y=35,label="Post-Training")
```

This is an attempt to use the geom_split_violin across multiple dates.  It doesn't work.
```{r}
ggplot(data=df.hr,aes(x=Date)) +
  geom_split_violin(data=subset(df.hr,Date==as.POSIXct('2023-10-01')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr,Date==as.POSIXct('2023-10-02')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr,Date==as.POSIXct('2023-10-03')),aes(x=Date,y=mean,fill=Group))
```
Here I use df.hr2 (Categorical date instead of POSIXct) which seems to resolve the issue, aside from dropping 10-6,10-7,and 10-8.  On the downside, it's fugly, and I'm not sure it's much more informative.
```{r}
ggplot(data=df.hr2,aes(x=Date)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-01')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-02')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-03')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-04')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-05')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-06')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-07')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-08')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-09')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-10')),aes(x=Date,y=mean,fill=Group)) +
  geom_split_violin(data=subset(df.hr2,Date==as.POSIXct('2023-10-11')),aes(x=Date,y=mean,fill=Group))
```

This is an attempt to use multiple geom_density functions to achieve the same end.  geom_density_ridges appears to be locked to a horizontal view, with no way to adjust height or distance.  I don't think this'll work.
```{r}
df.hr2 <- df.hr %>% mutate(Date=as.character(Date))
ggplot(data=df.hr2,aes(x=mean,y=Date)) +
  geom_density_ridges()
```
```{r}
df.hr2 <- df.hr %>% mutate(Date=as.character(Date))
ggplot(data=df.hr2,aes(x=Date,y=mean)) +
  geom_density(data=subset(df.hr2,Date='2023-10-01'),aes(y=mean))
```

```{r}
ggplot(data=df.hr.TR,aes(x=Date,y=mean)) +
  geom_violin()
```

