---
title: '20240102'
author: "Thomas FitzGerald"
date: "2024-07-01"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
library(plotly)
library(ggplot2)
library(stats)
library(multcomp)
library(emmeans)
library(lsmeans)
library(stringr)
library(lubridate)
```

The following code chunk will need to be changed for your file locations.  File descriptions to follow.
```{r}
dir.str <- 'C:/Users/Thoma/OneDrive/Desktop/Farm_1/'
df.ref <- read.csv(paste(dir.str,'animal_ref.csv',sep=''))
df.weather <- read.csv(paste(dir.str,'weather_2.csv',sep=''))
df.hr <- read.csv(paste(dir.str,'Pulse Data/pulse_dense_results.csv',sep=''))
df.milk <- read.csv(paste(dir.str,'EAF2AgSourceMilk/EAF_All.csv',sep=''))
df.milk2 <- read.csv(paste(dir.str,'BoviSync_2024-02-13 11_39.csv',sep=''))
df.greenfeed.rolling <- read.csv(paste(dir.str,'GreenFeed_rolling_averages.csv',sep=''))
df.weight <- read.csv(paste(dir.str,'cow_bodyweight.csv',sep=''))

df.actor <- read.csv(paste(dir.str,'Cow_Activity_Actor.csv',sep=''))
df.approach <- read.csv(paste(dir.str,'Cow_Activity_Approach.csv',sep=''))
df.exploration <- read.csv(paste(dir.str,'Cow_Activity_Exploration.csv',sep=''))
df.reactor <- read.csv(paste(dir.str,'Cow_Activity_Reactor.csv',sep=''))
```
df.ref: 
  .csv with columns animal_number(int),Treatment_Group(str),Experiment_Group(str),player_number(int),RFID(int)
  Required columns: animal_number (cow identifier), Treatment_Group (UTR/TR for Trained/Untrained), Experiment_Group(Group_1/Group_2)

df.weather: 
  .csv with columns DateTime(datetime),High temperature(int),Low temperature(int),Normal high temperature(int),Normal low temperature(int)
  Required columns: Date, High temperature & Low temperature (temperature in degrees C.)

df.hr: 
  .csv with columns Experiment_Group(str),Group(str),Time_Period(str),Date(date),HR_avg_bpm(int),Player_name(str),cow_id(int)
  Required columns: cow_id (same as animal_number in df.ref), HR_avg_bpm (Heart rate in beats per minute)

df.milk:  
  .csv with columns date(date),cow_id(int),butterfat(dbl),protein(dbl),lactose(dbl),mun(dbl)
  Required columns: cow_id (same as animal_number in df.ref), butterfat/protein/lactose (g/100g content in milk), mun (?)

df.milk2: 
  .csv with columns AMPM(str),AnEar(int),ShiftNum(int),MilkShif(dbl),DayTMilk(dbl),Group(str),Milk#(int),DIM(int),ShiftDate(date)
  Required columns: AnEar (same as animal_number in df.ref), DayTMilk(total milk yield in pounds per day.)

df.greenfeed.rolling
  Required columns: cow_id (same as animal_number in df.ref), dateStart (datetime containing date), goodDataDuration (total measurement time), durationCount(total greenfeed approaches), CO2MassFlow(), CH4MassFlow

df.weight: 
  Required columns: AnEar(same as animal_number in df.ref), Weight (lbs), Date(date of measurement)



The following code chunk formats our input data and combines it where necessary.  The following values are hard-coded and will likely need changing:

Experiment_Group: Group_1/Group_2
Treatment_Group: UTR/TR
Time_Period: pre-train, training, post-train.  df.milk, df.milk2, and df.greenfeed.rolling use hard-coded date ranges to determine which values fall in which range.  Also, please note that "training" and "post-training" periods are technically misnomers, since both occurred after the training period.

IMPORTANT: Samples were taken at different times, and the date ranges may vary between each dataframe.  Make sure to update each individually.

```{r}
df.ref <- df.ref %>% 
  mutate(cow_id=animal_number) %>%
  dplyr::select(cow_id,Treatment_Group,Experiment_Group)

df.weight <- df.weight %>% 
  mutate(Date=as.Date(Date, format='%m/%d/%Y')) %>%
  mutate(cow_id=AnEar) %>%
  group_by(cow_id) %>%
  summarize(Weight=mean(Weight,na.rm=T)/2.2)

df.weather <- df.weather %>%
  mutate(Date=as.POSIXct(DateTime,format=c("%m/%d/%Y"))) %>%
  mutate(Avg.temperature = (High.temperature+Low.temperature)/2) %>%
  dplyr::select(Date,Avg.temperature) 

df.milk2 <- df.milk2 %>%
  mutate(cow_id=AnEar) %>%
  subset(cow_id %in% df.ref$cow_id) %>%
  mutate(Date=as.Date(ShiftDate, format('%Y-%m-%d'))) %>%
  mutate(Experiment_Group = case_when(cow_id %in% subset(df.ref,Experiment_Group=='Group_1')$animal_number ~ 'Group_1',
                       cow_id %in% subset(df.ref,Experiment_Group=='Group_2')$animal_number ~ 'Group_2')) %>%
  mutate(Treatment_Group = case_when(cow_id %in% subset(df.ref,Treatment_Group=='TR')$animal_number ~ 'TR',
                           cow_id %in% subset(df.ref,Treatment_Group=='UTR')$animal_number ~ 'UTR')) %>%
  mutate(Time_Period = case_when(Date >= '2023-08-28' & Date <= '2023-09-05' ~ 'pre-train',
                                 Date >= '2023-09-06' & Date <= '2023-09-08' ~'training',
                                 Date >= '2023-09-11' & Date <= '2023-09-14' ~ 'post-train',
                                 
                                 Date >= '2023-10-01' & Date <= '2023-10-02' ~ 'pre-train',
                                 Date >= '2023-10-03' & Date <= '2023-10-05' ~'training',
                                 Date >= '2023-10-06' & Date <= '2023-10-17' ~ 'post-train')) %>%
  subset(!is.na(Time_Period)) %>%
  mutate(Time_Period=str_replace(Time_Period, 'pre-train','Pre-Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'training','Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'post-train','Post-Training')) %>%
  #subset(Time_Period!='train') %>%
  relocate(Experiment_Group,Treatment_Group,Time_Period,Date,cow_id,DayTMilk) %>%  
  dplyr::select(c(Experiment_Group,Treatment_Group,Time_Period,Date,cow_id,DayTMilk,DIM)) %>%
  arrange(cow_id,Date)




df.weight <- merge(df.weight,
                   dplyr::select(left_join(df.ref,dplyr::select(df.milk2, c(cow_id,Date,DIM)),by = join_by(cow_id)) %>% subset((Experiment_Group=='Group_1' & Date=='2023-09-03') | (Experiment_Group=='Group_2' & Date=='2023-10-01')), c(cow_id,DIM)) %>% group_by(cow_id), 
                   all = TRUE)

df.ref <- merge(df.ref,df.weight, all = TRUE)

df.milk2 <- left_join(df.ref,
          dplyr::select(df.milk2, c(cow_id,Date,Time_Period,DayTMilk)),by = join_by(cow_id))

df.hr <- df.hr %>% 
  dplyr::select(c(cow_id,Date,Time_Period,HR_avg_bpm)) %>%
  left_join(df.ref, by = join_by(cow_id)) %>%
  relocate(cow_id,Experiment_Group,Treatment_Group,Time_Period,Date,HR_avg_bpm) %>%
  mutate(Time_Period=str_replace(Time_Period, 'pre-train','Pre-Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'training','Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'post-train','Post-Training')) %>%
  arrange(cow_id,Date)



df.milk <- df.milk %>%
  subset(butterfat != 'Short Sample') %>%
  mutate(Date=as.Date(date, format='%m/%d/%Y')) %>%
  dplyr::select(-c(date,date2)) %>%
  left_join(df.ref, by = join_by(cow_id)) %>%
  mutate(Time_Period = case_when(Date >= '2023-08-28' & Date <= '2023-08-29' ~ 'pre-train',
                                 Date >= '2023-09-06' & Date <= '2023-09-08' ~'training',
                                 Date >= '2023-09-11' & Date <= '2023-09-14' ~ 'post-train',
                                 
                                 Date >= '2023-09-25' & Date <= '2023-09-26' ~ 'pre-train',
                                 Date >= '2023-10-03' & Date <= '2023-10-05' ~'training',
                                 Date >= '2023-10-06' & Date <= '2023-10-17' ~ 'post-train')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'pre-train','Pre-Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'training','Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'post-train','Post-Training')) %>%
  mutate(butterfat = as.double(butterfat)) %>%
  subset(!is.na(Time_Period)) %>%
  relocate(Date,Time_Period,Treatment_Group) %>%
  relocate(cow_id,Experiment_Group,Treatment_Group,Time_Period,Date,Weight,DIM) %>%  
  group_by(cow_id,Experiment_Group,Treatment_Group,Time_Period,Date,Weight,DIM) %>% 
  summarize(butterfat=mean(butterfat,is.na=T),protein=mean(protein,is.na=T),lactose=mean(lactose,is.na=T),mun=mean(mun,is.na=T)) %>%
  arrange(cow_id,Date)

df.milk.combined <- merge(merge(df.milk,df.milk2 %>% dplyr::select(c(cow_id,Date,DayTMilk))),df.ref) %>%
  mutate(milk_yield_kg = (DayTMilk/2.2)) %>%
  mutate(butterfat_kg = (butterfat*milk_yield_kg)/100) %>%
  mutate(protein_kg = (protein*milk_yield_kg)/100) %>%
  mutate(lactose_kg = (lactose*milk_yield_kg)/100) %>%
  dplyr::select(cow_id,Date,Experiment_Group,Treatment_Group,Time_Period,milk_yield_kg,butterfat_kg,protein_kg,lactose_kg,butterfat,protein,lactose,mun,Weight,DIM) %>%
  group_by(cow_id,Date,Experiment_Group,Treatment_Group,Time_Period) %>%
  summarize(yield=mean(milk_yield_kg),
            butterfat_kg=mean(butterfat_kg),
            protein_kg=mean(protein_kg),
            lactose_kg=mean(lactose_kg),
            butterfat=mean(butterfat),
            protein=mean(protein),
            lactose=mean(lactose),
            mun=mean(mun),
            ECMV=(.327*yield) + (12.95*butterfat_kg) + (7.20*protein_kg),
            Weight=mean(Weight),
            DIM=mean(DIM)) %>%
  mutate(Time_Period=str_replace(Time_Period, 'pre-train','Pre-Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'training','Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'post-train','Post-Training')) %>%
  arrange(cow_id,Experiment_Group,Time_Period,Treatment_Group)

df.greenfeed.rolling <- df.greenfeed.rolling %>%
  dplyr::select(c(farmName,cow_id,dateStart,goodDataDuration,durationCount,CO2MassFlow,CH4MassFlow)) %>%
  subset(farmName!='QC_Test ') %>%
  mutate(Date=as.Date(dateStart, format='%m/%d/%Y')) %>%
  mutate(goodDataDuration=
    as.integer(substr(goodDataDuration,0,1))*3600 +
    as.integer(substr(goodDataDuration,3,4))*60 +
    as.integer(substr(goodDataDuration,6,7))) %>%
  left_join(df.ref, by = join_by(cow_id)) %>%
  mutate(Time_Period = case_when(Experiment_Group=='Group_1' & Date >= '2023-09-03' & Date <= '2023-09-05' ~ 'pre-train',
                                 Experiment_Group=='Group_1' & Date >= '2023-09-06' & Date <= '2023-09-08' ~'training',
                                 Experiment_Group=='Group_1' & Date >= '2023-09-07'                        ~ 'post-train',
                                 
                                 Experiment_Group=='Group_2'                        & Date <= '2023-10-03' ~ 'pre-train',
                                 Experiment_Group=='Group_2' & Date >= '2023-10-03' & Date <= '2023-10-05' ~'training',
                                 Experiment_Group=='Group_2' & Date >= '2023-10-04' & Date <= '2023-10-17' ~ 'post-train')) %>%
  subset(!is.na(Time_Period)) %>%
  mutate(CO2=CO2MassFlow) %>%
  mutate(CH4=CH4MassFlow) %>%
  mutate(Time_Period=str_replace(Time_Period, 'pre-train','Pre-Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'training','Training')) %>%
  mutate(Time_Period=str_replace(Time_Period, 'post-train','Post-Training')) %>%
  dplyr::select(cow_id,Date,Experiment_Group,Treatment_Group,Time_Period,CO2,CH4,goodDataDuration,durationCount,Weight,DIM) %>%
  relocate(cow_id,Experiment_Group,Treatment_Group,Time_Period,Date,CO2,CH4) %>%
  arrange(cow_id,Date)

df.efficiency <- merge(merge(
  df.milk2 %>% group_by(cow_id,Experiment_Group,Treatment_Group,Time_Period) %>% summarize(yield=mean(DayTMilk/2.2)),
  df.greenfeed.rolling %>% group_by(cow_id,Experiment_Group,Treatment_Group,Time_Period) %>% summarize(CH4=mean(CH4))),
     df.weight) %>%
  mutate(CH4_BW=CH4/Weight) %>%
  mutate(yield_bw=yield/Weight) %>%
  mutate(CH4_yield=CH4/yield)

df.behavior <- left_join(
left_join(df.actor %>% mutate(cow_id=animal_number,actor=Total) %>% dplyr::select(cow_id,Exp_Group,actor),
df.reactor %>% mutate(cow_id=animal_number,reactor=Total) %>% dplyr::select(cow_id,Exp_Group,reactor)),
left_join(df.approach %>% mutate(cow_id=animal_number,approach=Total) %>% dplyr::select(cow_id,Exp_Group,approach),
df.exploration %>% mutate(cow_id=animal_number,exploration=Total) %>% dplyr::select(cow_id,Exp_Group,exploration))
)

df.behavior.proportion <- df.behavior %>%
  group_by(Exp_Group) %>% 
  mutate(count=1) %>%
  summarize(count=sum(count),
          actor=sum(actor),
          reactor=sum(reactor),
          approach=sum(approach),
          exploration=sum(exploration)) %>%
  subset(!is.na(actor))

```

This code block converts pre-training response variables to covariates.
```{r}
df.hr.nopt <- left_join(
  df.hr %>% subset(Time_Period!='Pre-Training'),
df.hr %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(pt_HR_avg_bpm=mean(HR_avg_bpm)),
by = join_by(cow_id))

df.greenfeed.rolling.nopt <-  left_join(
  df.greenfeed.rolling %>% subset(Time_Period!='Pre-Training'),
  df.greenfeed.rolling %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(pt_CO2=mean(CO2),
            pt_CH4=mean(CH4),
            pt_goodDataDuration=mean(goodDataDuration),
            pt_durationCount=mean(durationCount)),
  by = join_by(cow_id))

df.milk.combined.nopt <- left_join(
  df.milk.combined %>% subset(Time_Period!='Pre-Training'),
df.milk.combined %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(pt_yield=mean(yield),
pt_butterfat_kg=mean(butterfat_kg),
pt_protein_kg=mean(protein_kg),
pt_lactose_kg=mean(lactose_kg),
pt_butterfat=mean(butterfat),
pt_protein=mean(protein),
pt_lactose=mean(lactose),
pt_mun=mean(mun),
pt_ECMV=mean(ECMV)),
by = join_by(cow_id))

df.milk.nopt <- left_join(
  df.milk %>% subset(Time_Period!='Pre-Training'),
df.milk %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(
pt_butterfat=mean(butterfat),
pt_protein=mean(protein),
pt_lactose=mean(lactose),
pt_mun=mean(mun)),
by = join_by(cow_id))

df.milk2.nopt <- left_join(
  df.milk2 %>% subset(Time_Period!='Pre-Training'),
df.milk2 %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(pt_yield=mean(DayTMilk)/2.2),
by = join_by(cow_id))

df.efficiency.nopt <- left_join(
  df.efficiency %>% subset(Time_Period!='Pre-Training'),
df.efficiency %>% subset(Time_Period=='Pre-Training') %>%
  group_by(cow_id) %>%
  summarize(pt_yield=mean(yield),
            pt_CH4=mean(CH4),
            pt_CH4_BW=mean(CH4_BW),
            pt_yield_bw=mean(yield_bw),
            pt_CH4_yield=mean(CH4_yield)),
by = join_by(cow_id))
```

This is used for checking sample numbers from each dataset.
```{r}
# print('Ref')
# table(df.ref$Treatment_Group, df.ref$Experiment_Group)
# print('Heart_Rate')
# table(df.hr$Time_Period,df.hr$Treatment_Group, df.hr$Experiment_Group)
# print('Metabolism')
#table(df.greenfeed.rolling$Time_Period,df.greenfeed.rolling$Treatment_Group, df.greenfeed.rolling$Experiment_Group)
# print('Metabolism_Averages')
# table(df.greenfeed.rolling$Time_Period,df.greenfeed.rolling$Treatment_Group, df.greenfeed.rolling$Experiment_Group)
# table(df.greenfeed.rolling.nopt$Time_Period,df.greenfeed.rolling.nopt$Treatment_Group, df.greenfeed.rolling.nopt$Experiment_Group)
# print('Milk')
# table(df.milk$Time_Period,df.milk$Treatment_Group, df.milk$Experiment_Group)
# table(df.milk2$Time_Period,df.milk2$Treatment_Group, df.milk2$Experiment_Group)
# table(df.milk.combined$Time_Period,df.milk.combined$Treatment_Group, df.milk.combined$Experiment_Group)
# table(df.milk.combined.nopt$Time_Period,df.milk.combined.nopt$Treatment_Group, df.milk.combined.nopt$Experiment_Group)
# print('Milk_Averages')
# table(df.milk.combined.averages$Time_Period,df.milk.combined.averages$Group, df.milk.combined.averages$Experiment_Group)
# print('Efficiency')
# table(df.efficiency$Time_Period,df.efficiency$Treatment_Group, df.efficiency$Experiment_Group)
# table(df.efficiency.nopt$Time_Period,df.efficiency.nopt$Treatment_Group, df.efficiency.nopt$Experiment_Group)
```

This block gets weight, and DIM averages for each experimental group.
```{r}
df.hr.test <- df.hr %>% dplyr::select(cow_id,Experiment_Group,Treatment_Group) %>% distinct() %>% arrange(Experiment_Group,Treatment_Group)
df.greenfeed.test <- df.greenfeed.rolling %>% dplyr::select(cow_id,Experiment_Group,Treatment_Group) %>% distinct() %>% arrange(Experiment_Group,Treatment_Group)
df.milk.test <- df.milk %>% dplyr::select(cow_id,Experiment_Group,Treatment_Group) %>% distinct() %>% arrange(Experiment_Group,Treatment_Group) %?% 
df.milk2.test <- df.milk2 %>% dplyr::select(cow_id,Experiment_Group,Treatment_Group) %>% distinct() %>% arrange(Experiment_Group,Treatment_Group)

table(df.ref$Experiment_Group,df.ref$Treatment_Group)
table(df.hr.test$Experiment_Group,df.hr.test$Treatment_Group)
table(df.greenfeed.test$Experiment_Group,df.greenfeed.test$Treatment_Group)
table(df.milk.test$Experiment_Group,df.milk.test$Treatment_Group)
table(df.milk2.test$Experiment_Group,df.milk2.test$Treatment_Group)

df.ref %>% 
  group_by(Experiment_Group,Treatment_Group) %>%
  summarize(Weight=mean(Weight,na.rm=TRUE),
            DIM=mean(DIM,na.rm=TRUE))
df.ref %>% 
  group_by(Treatment_Group) %>%
  summarize(Weight=mean(Weight,na.rm=TRUE),
            DIM=mean(DIM,na.rm=TRUE))
```


```{r}
print_experiment_results <- function(df,var.name,nopt=FALSE){
  #Takes a dataframe (df.hr, df.milk.combined,df.greenfeed.rolling,df.efficiency) as input.  
  #var.name is the response variable to test.
  if(nopt){
    covar.name <- paste('pt_',var.name,sep='')
    df <- df %>% mutate(Treatment_Group=as.character(Treatment_Group),Time_Period=as.character(Time_Period)) %>% rename(var = var.name,covar = covar.name)
  }else{
    df <- df %>% mutate(Treatment_Group=as.character(Treatment_Group),Time_Period=as.character(Time_Period)) %>% rename(var = var.name)
  }
  
  print(paste('SD,SEM',
              sd(df$var),
  sd(df$var)/sqrt(nrow(df)),
  sep=' '))
  
  if(!nopt){
  print(paste(('pre-train'),
  mean(subset(df,Treatment_Group=='UTR'&Time_Period %in% c('pre-train','Pre-Training'))$var,na.rm=T),
  mean(subset(df,Treatment_Group=='TR'&Time_Period %in% c('pre-train','Pre-Training'))$var,na.rm=T),sep=' '))
  }
  
  print(paste(('training'),
  mean(subset(df,Treatment_Group=='UTR'&Time_Period %in% c('training','Training'))$var),
  mean(subset(df,Treatment_Group=='TR'&Time_Period%in% c('training','Training'))$var),sep=' '))
  
  print(paste(('post-train'),
  mean(subset(df,Treatment_Group=='UTR'&Time_Period %in% c('post-train','Post-Training'))$var),
  mean(subset(df,Treatment_Group=='TR'&Time_Period %in% c('post-train','Post-Training'))$var),sep=' '))
  
  #try(print(t.test(data=df %>% subset(Time_Period %in% c('pre-train','Pre-Training')),var~Group)))
  #try(print(t.test(data=df %>% subset(Time_Period %in% c('training','Training')),var~Group)))
  #try(print(t.test(data=df %>% subset(Time_Period %in% c('post-train','Post-Training')),var~Group)))
  
  if(nopt){
    print(anova(lm(data=df,formula = var ~ Treatment_Group +  Time_Period + Weight + DIM + covar + Treatment_Group*Time_Period, contrasts = list(Time_Period = 'contr.treatment'))))
  } else{
    print(anova(lm(data=df,formula = var ~ Treatment_Group +  Time_Period + Weight + DIM + Treatment_Group*Time_Period, contrasts = list(Time_Period = 'contr.treatment'))))
  }
}
```


```{r}
print_experiment_results_2 <- function(df,var.name,nopt=FALSE){
  if(nopt){
    covar.name <- paste('pt_',var.name,sep='')
    df <- df %>% mutate(Treatment_Group=as.character(Treatment_Group),Time_Period=as.character(Time_Period)) %>% rename(var = var.name,covar = covar.name)
  }else{
    df <- df %>% mutate(Treatment_Group=as.character(Treatment_Group),Time_Period=as.character(Time_Period)) %>% rename(var = var.name)
  }
  print(paste('--------------------',var.name,'--------------------',sep=''))
  if(nopt){
  lm.obj <- lm(data=df,formula = var ~ Treatment_Group + Time_Period + Weight + DIM + covar + Treatment_Group*Time_Period, contrasts = list(Time_Period = 'contr.treatment'))
    }else{
  lm.obj <- lm(data=df,formula = var ~ Treatment_Group + Time_Period + Weight + DIM + Treatment_Group*Time_Period, contrasts = list(Time_Period = 'contr.treatment'))
  }
    print('--------------------ANOVA--------------------')
  print(anova(lm.obj))
  print('--------------------Contrasts--------------------')
  print(contrast(emmeans(lm.obj, ~ Time_Period + Treatment_Group), method='dunnett'))
  print('--------------------Model Summary--------------------')
  print(summary(lm.obj))
  print(lsmeans(lm.obj, c('Experiment_Group, Group','Time_Period')))
}
```
```{r}
geom_split_violin <- function(mapping = NULL,
                              data = NULL,
                              stat = "ydensity",
                              position = "identity",
                              ...,
                              draw_quantiles = NULL,
                              trim = TRUE,
                              scale = "area",
                              na.rm = FALSE,
                              show.legend = NA,
                              inherit.aes = TRUE) {
  ggplot2::layer(
    data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin,
    position = position, show.legend = show.legend, inherit.aes = inherit.aes,
    params = list(
      trim = trim, scale = scale, draw_quantiles = draw_quantiles,
      na.rm = na.rm, ...
    )
  )
}

#' @format NULL
#' @usage NULL
GeomSplitViolin <- ggplot2:::ggproto("GeomSplitViolin",
                                     ggplot2::GeomViolin,
                                     draw_group = function(self, data, ..., draw_quantiles = NULL) {
                                       data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
                                       grp <- data[1, "group"]
                                       newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
                                       newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
                                       newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
                                       if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
                                         stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
                                                                                   1))
                                         quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
                                         aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
                                         aesthetics$alpha <- rep(1, nrow(quantiles))
                                         both <- cbind(quantiles, aesthetics)
                                         quantile_grob <- GeomPath$draw_panel(both, ...)
                                         ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
                                       }
                                       else {
                                         ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
                                       }
                                     }
)

```

```{r}
df.test <- subset(df.hr.nopt,Experiment_Group=='Group_1')
df.test <- subset(df.hr.nopt,Experiment_Group=='Group_2')
```

```{r}
print_experiment_results(df.hr.nopt,'HR_avg_bpm',TRUE)
print_experiment_results_2(df.hr.nopt,'HR_avg_bpm',TRUE)
```

Co2/Methane
```{r}
print_experiment_results(df.greenfeed.rolling.nopt,'CO2',TRUE)
print_experiment_results_2(df.greenfeed.rolling.nopt,'CO2',TRUE)
```
```{r}
print_experiment_results(df.greenfeed.rolling.nopt,'CH4',TRUE)
print_experiment_results_2(df.greenfeed.rolling.nopt,'CH4',TRUE)
```
Milk Output
```{r}
print_experiment_results(df.milk2.nopt %>% mutate(yield=DayTMilk/2.2),'yield',TRUE)
print_experiment_results_2(df.milk2.nopt %>% mutate(yield=DayTMilk/2.2),'yield',TRUE)
```
```{r}
print_experiment_results(df.milk.combined,'butterfat_kg')
#print_experiment_results_2(df.milk.combined,'butterfat_kg')
```
```{r}
print_experiment_results(df.milk.combined,'protein_kg')
print_experiment_results_2(df.milk.combined,'protein_kg')
```
```{r}
print_experiment_results(df.milk.combined,'lactose_kg')
print_experiment_results_2(df.milk.combined,'lactose_kg')
```
Milk Composition (Lactose,Protein,Butterfat,mun)

```{r}
print_experiment_results(df.milk.nopt,'butterfat',TRUE)
#print_experiment_results_2(df.milk.nopt,'butterfat',TRUE)
```
```{r}
print_experiment_results(df.milk.nopt,'protein',TRUE)
print_experiment_results_2(df.milk.nopt,'protein',TRUE)
```
```{r}
print_experiment_results(df.milk.nopt,'lactose',TRUE)
print_experiment_results_2(df.milk.nopt,'lactose',TRUE)
```
```{r}
print_experiment_results(df.milk.nopt,'mun',TRUE)
#print_experiment_results_2(df.milk.nopt,'mun',TRUE)
```

```{r}
print_experiment_results(df.milk.combined.nopt,'ECMV',TRUE)
print_experiment_results_2(df.milk.combined.nopt,'ECMV',TRUE)
```

```{r}
print_experiment_results(df.efficiency.nopt,'CH4_BW',TRUE)
print_experiment_results_2(df.efficiency.nopt,'CH4_BW',TRUE)
```
```{r}
#print_experiment_results(df.efficiency,'yield_bw')
#print_experiment_results_2(df.efficiency,'yield_bw')
print_experiment_results(df.efficiency.nopt,'yield_bw',TRUE)
print_experiment_results_2(df.efficiency.nopt,'yield_bw',TRUE)
```

```{r}
#print_experiment_results(df.efficiency,'CH4_yield')
#print_experiment_results_2(df.efficiency,'CH4_yield')
print_experiment_results(df.efficiency.nopt,'CH4_yield',TRUE)
#print_experiment_results_2(df.efficiency.nopt,'CH4_yield',TRUE)
```

```{r}
print_experiment_results(df.greenfeed.rolling.nopt,'goodDataDuration', TRUE)
print_experiment_results_2(df.greenfeed.rolling.nopt,'goodDataDuration')
```

```{r}
print_experiment_results(df.greenfeed.rolling.nopt,'durationCount',TRUE)
print_experiment_results_2(df.greenfeed.rolling.nopt,'durationCount',TRUE)
```

```{r}
sd(df.approach$var)/sqrt(nrow(df.approach))
```

```{r}
subset(df.approach, Player_Number %in% c("TR_Summary","UTR_Summary","UNKNOWN_Summary","NIS_Summary"))$Total
subset(df.exploration, Player_Number %in% c("TR_Summary","UTR_Summary","UNKNOWN_Summary","NIS_Summary"))$Total
subset(df.actor, Player_Number %in% c("TR_Summary","UTR_Summary","UNKNOWN_Summary","NIS_Summary"))$Total
subset(df.reactor, Player_Number %in% c("TR_Summary","UTR_Summary","UNKNOWN_Summary","NIS_Summary"))$Total
```

```{r}
t.test(subset(df.approach,Exp_Group %in% c("TR","UTR"))$Total)
t.test(subset(df.exploration,Exp_Group %in% c("TR","UTR"))$Total)
t.test(subset(df.actor,Exp_Group %in% c("TR","UTR"))$Total)
t.test(subset(df.reactor,Exp_Group %in% c("TR","UTR"))$Total)
```

```{r}
df.behavior.proportion %>% 
  subset(Exp_Group %in% c('UTR','TR')) %>%
  mutate(actor=actor/count,
         reactor=reactor/count,
         approach=approach/count,
         exploration=exploration/count)
```

```{r}
ggplot(data=df.summary %>% 
         mutate(Time_Period= str_replace(Time_Period, 'Pre-Training','Training')) %>%
         mutate(Time_Period = factor(Time_Period, levels=c('Pre-Training','Training','Post-Training'))) %>% 
         mutate(Group= factor(Group,levels=c('UTR','TR'))) ,aes(x=Time_Period)) +  
  geom_split_violin(aes(x=Time_Period,y=HR_avg_bpm,fill=Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Daily Avg. Heart Rate (bpm)") +
  xlab("Time Period") +
  theme_classic() +
  theme(axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position='none')
```

```{r}
ggplot(data=df.hr.nopt %>% 
         mutate(Time_Period = factor(Time_Period, levels=c('Pre-Training','Training','Post-Training'))) %>% 
         mutate(Treatment_Group= factor(Treatment_Group,levels=c('UTR','TR'))) ,aes(x=Time_Period)) +  
  geom_split_violin(aes(x=Time_Period,y=HR_avg_bpm,fill=Treatment_Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Average Heart Rate (bpm)") +
  xlab("Time Period") +
  theme_classic() +
  ggtitle("Heart Rate") +
  theme(plot.title = element_text(hjust = 0.5),
        axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position = '')
```

```{r}
ggplot(data=df.greenfeed.rolling.nopt %>% 
         mutate(Time_Period = factor(Time_Period, levels=c('Pre-Training','Training','Post-Training'))) %>% 
         mutate(Treatment_Group= factor(Treatment_Group,levels=c('UTR','TR'))) ,aes(x=Time_Period)) +  
  geom_split_violin(aes(x=Time_Period,y=CO2,fill=Treatment_Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("CO2 Output (g/day)") +
  xlab("Time Period") +
  theme_classic() +
  ggtitle("CO2") +
  theme(plot.title = element_text(hjust = 0.5),
        axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position = '')
```

```{r}
ggplot(data=df.greenfeed.rolling.nopt %>% 
         mutate(Time_Period = factor(Time_Period, levels=c('Pre-Training','Training','Post-Training'))) %>% 
         mutate(Treatment_Group= factor(Treatment_Group,levels=c('UTR','TR'))) ,aes(x=Time_Period)) +  
  geom_split_violin(aes(x=Time_Period,y=CH4,fill=Treatment_Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("CH4 Output (g/day)") +
  xlab("Time Period") +
  theme_classic() +
  ggtitle("CH4") +
  theme(plot.title = element_text(hjust = 0.5),
        axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2))
```
```{r}
ggplot(data=df.greenfeed.rolling %>% 
         mutate(Time_Period = factor(Time_Period, levels=c('Pre-Training','Training','Post-Training'))) %>% 
         mutate(Group= factor(Group,levels=c('UTR','TR'))) ,aes(x=Time_Period)) +  
  geom_split_violin(aes(x=Time_Period,y=durationCount,fill=Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Visits per Day") +
  xlab("Time Period") +
  theme_classic() +
  theme(legend.position='none')
```
```{r}
ggplot(data=df.efficiency %>% mutate(Time_Period=factor(Time_Period,levels=c('Training','Post-Training'))),
  aes(x=Time_Period)) +  
  
  geom_split_violin(aes(x=Time_Period,y=yield_bw,fill=Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Milk Efficiency (kg yield/BW)") +
  xlab("Time Period") +
  theme_classic() +
  theme(axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position='none')
```
```{r}
ggplot(data=subset(df.greenfeed.rolling,Time_Period=='Post-Training')) +  
  geom_split_violin(aes(x=Time_Period,y=durationCount,fill=Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Visits per Day") +
  xlab("Time Period") +
  theme_classic() +
  theme(axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position='none')
```
```{r}
ggplot(merge(df.summary %>% mutate(Date=as.Date(Date, format='%m/%d/%Y')),df.weather %>% mutate(Date=as.Date(Date))), aes(x=Avg.temperature,y=HR_avg_bpm, color=Group)) +
  geom_point() + 
  scale_color_brewer(palette="Set1")

cor(df.merged$Avg.temperature,df.merged$HR_avg_bpm)
cor(subset(df.merged, Group=='UTR')$Avg.temperature,subset(df.merged, Group=='UTR')$HR_avg_bpm)
cor(subset(df.merged, Group=='TR')$Avg.temperature,subset(df.merged, Group=='TR')$HR_avg_bpm)
```

```{r}
print_experiment_results(df.hr.nopt,'HR_avg_bpm',TRUE)
lm.obj <- lm(data=df.hr.nopt, HR_avg_bpm ~ Group + Experiment_Group + Time_Period + pt_HR_avg_bpm + Group*Time_Period)
summary(lm.obj)
```

```{r}
print_experiment_results(df.milk.combined.nopt,'yield',TRUE)
print(anova(lm(data=df.milk.combined.nopt,formula = yield ~ Group + pt_yield + Group*Time_Period, contrasts = list(Time_Period = 'contr.treatment'))))
lm.obj <- lm(data=df.milk.combined.nopt, butterfat ~ Group + pt_butterfat)
summary(lm.obj)
lm.obj <- lm(data=df.milk.combined.nopt, butterfat ~ Group + Experiment_Group + pt_butterfat)
summary(lm.obj)
```

```{r}
ggplot(data=subset(df.greenfeed.rolling,Experiment_Group=='Group_1')) +  
  geom_split_violin(aes(x=Time_Period,y=CO2,fill=Group)) + 
  scale_fill_brewer(palette="Set2") +
  ylab("Average Heart Rate") +
  xlab("Time Period") +
  theme_classic() +
  theme(axis = element_text(size=12),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16),
        axis.line=element_line(size=2),
        legend.position='none')
```


